---
title: "Demonstrating Metadata Extraction for DataCite"
format: html
---

# Working with Datacite Metadata

DataCite is an international organization that provides persistent identifiers 
(DOIs) for research data and other research outputs. Their metadata handling 
process is crucial for ensuring the discoverability, accessibility, and 
reusability of research outputs. DataCite's metadata schema is designed to 
capture essential information about research outputs, including titles, creators, 
publication year, and resource type, among others. This comprehensive metadata 
framework facilitates the accurate and consistent description of data, making 
it easier for researchers, institutions, and funders to manage and track the 
impact of their research outputs. By standardizing metadata across various 
disciplines and repositories, DataCite plays a pivotal role in enhancing the 
interoperability of research data, supporting open science initiatives, and 
promoting data citation and reuse.


```{r}
# Required libraries
#library(eurostat)
devtools::load_all()
# Fetch the dataset here using get_eurostat_sdmx function
dataset <- get_eurostat_sdmx(id = "cult_emp_sex")

```

The function `get_eurostat_sdmx` fetches required data with id `cult_emp_sex`. The fetched data includes metadata and  can be accessed using `attr()` function as below.

```{r}

# Assigning the 
metadata <- attr(dataset, "metadata")
metadata
# Ensure you replace the agency and id with actual values or examples relevant to your context
```



